% Author: Isaac H. Lopez Diaz <isaac.lopez@upr.edu>
% Description: Presentation for CCOM 6050

\documentclass{beamer}

\usepackage{dirtytalk}

% Document info
\title{A Reflective language with Dependent Types}
\author{Isaac H. Lopez Diaz\inst{1}}
\institute
{
\inst{1}
Department of Computer Science\\
University of Puerto Rico at Rio Piedras
}

%% DOC START %%
\begin{document}
\maketitle

% FRAME 1 %
\begin{frame}
  \frametitle{Overview}
  \begin{itemize}
  \item History of Programming Languages
  \item Reflective Languages
  \item Motivation
  \item Live Demo
  \item Questions
  \end{itemize}
\end{frame}

% FRAME 2 %
\begin{frame}
  \frametitle{History of PL}
  \begin{itemize}
  \item $\lambda$-calculus by Alonzo Church
  \item Golden Years (1960s-1980s): Assembly, Fortran, Lisp, C
  \item Modern Era: Python, Java, JavaScript, Rust, OCaml
  \end{itemize}
  
\end{frame}

% FRAME 3 %
\begin{frame}
  \frametitle{Type Systems}
  \begin{itemize}
  \item Simply Typed $\lambda$-calculus by Alonzo Church
  \item Static Typing - simple solution to catch type errors at compile time.
  \item Hindley-Milner - introduced type inference and polymorphism
  \item Advanced Type Systems - type classes, GADTs, higher-kinded types, OOP, etc.
  \end{itemize}
\end{frame}

% FRAME 4 %
\begin{frame}
  \frametitle{Dependent Types}
  \begin{itemize}
  \item Types depend on terms (values).
  \item Types are first-class citizens.
  \item Classic example: Array Length
  \item Static typing with dynamic properties (not true).
  \end{itemize}
  
\end{frame}

% FRAME 5 %
\begin{frame}
  \frametitle{Reflective languages}
  \say{The evaluator, which determines the meaning of expressions in a programming language, is just another program.} - (SICP) \\   
  \begin{itemize}
  \item What is it?
  \item What does reflective mean?
  \item Infinite towers
  \end{itemize}
\end{frame}

% FRAME 6 %
\begin{frame}
  \frametitle{Reflective languages (cont.)}
  \begin{itemize}
  \item In late 1990s and early 2000s significant amount of languages appeared.
  \item Daniel P. Friedman stopped working because: \say{It burned my brain too much.}
  \end{itemize}
  
\end{frame}

% FRAME 7 %
\begin{frame}
  \frametitle{Motivation}
  \begin{itemize}
  \item Master Thesis/Project
  \item Allows for precise specifications
  \item Verified evaluators
  \item Deep insights on semantics
  \item Live demo
  \end{itemize}
  
\end{frame}

% REFERENCES
\begin{frame}[allowframebreaks]
  \frametitle{References}
\nocite*
\bibliographystyle{acm}
\bibliography{refs}
\end{frame}
\end{document}
%% DOC END %%
